\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-1.5in}
\addtolength{\textheight}{1.75in}

\title{Project Week on 3. Semester}

\begin{document}
\maketitle
\section{Working plan}
Now it is project week and I suggest that we work from morning until evening the days it is possible, please fill in when you are busy with something else + what the others should do on 'your' project.
3 things to work on: Interaction design (Jesus hands out who does what), web design (Dennis writes intro + index page, Theis writes about the module pages, Jesus writes about optimising for small screen devices). PRO3 (Restructure setup to 14 days sprints and write what is missing to launch phase. Theis hands out who does what in the first sprint).
\subsection{Monday}
Dennis is having a meeting with the other teams from 10-11.
\\Theis + Paulo meets in the basement when?
\\Paulo will be at the basement at 8.
\\Everyone in the basement from 12 to 20.
\subsection{Tuesday}
Everyone meets in the basement at 8 and continue until 20.
\subsection{Wednesday}
Meet in the basement and setup our stuffy at 9 where after we drive to B and O.
\\ \textit{If Dennis got a car, he can drive, otherwise the Black BM will take us to Struer}
\\ Black BM will be full of gas to go everywhere.
\\ Dennis is gone from 14.30 to 16.30 (upgrading his teeth).
\\ Paulo will make cake for this day so there will be just two eating cake, since Dennis just upgraded is teeth.
\subsection{Thursday}
Everyone meets in the basement at 8 and continue until 20.
\\ Theis is working from 16.00
\subsection{Friday}
Dennis is having a meeting with the other teams from 10-11.
\\ Theis is going to the doctor to check his eyes from 9:45
\\ Theis is working from 16.00
\\ Maybe Burgers in the evening (depends on when Theis is off work).
\\ Burgers Sounds awesome for Paulo.
\subsection{Saturday}
Should we plan some work here ?\\
I think we should see first how the work goes during the week.\\
\subsection{Sunday}
Should we plan some work here ?\\
I think we should see first how the work goes during the week and saturday if needed.\\

\section{Who does what?}
\subsection{Interaction Design}

\begin{tabular}{ | p{8cm} | c | p{5cm} |}
\hline
Description & Responsible & Due Date \\ \hline
Front page & Jesus & 28/11/2011\\ \hline
Table of content & Jesus & Done \\ \hline
Introduction & Jesus & Done\\ \hline
Problem statement for PRO3 project & Theis & \\ \hline
Description of the PRO3 task & Theis & \\ \hline
Stakeholder description & Jesus  & Done\\ \hline
Argued Usability goals & Dennis & Done just needed to be read through\\ \hline
User Experience goals &  Dennis  & Done just needed to be read through\\ \hline
Description of your prototypes & Theis & \\ \hline
Interactive participatory design with users & Dennis  & \\ \hline
Description of your final usability test of the product & Jesus & We should do a usability test with Jans first. \\ \hline
Conclusion (answer to the problem statement) & Jesus  & Waiting for the problem statement.\\ \hline
Process Description & Jesus & 30/11/2011\\ \hline
Reference (literature) & Jesus  &  02/12/2011\\ \hline
Report Finished Read Through Report & ALL & 09/12/2011\\ \hline
Printing &  & 12/12/2011\\ \hline
Report Delivery at 16th of December & Jesus & 12/12/2011 \\ \hline
\hline
\end{tabular}

\subsection{Web}
\textbf{ALL:} Write about the sections described in the HTML report. Theis: Design of the modules page(s), Jesus: Small screen optimization, Dennis: Index page + intro + environment.
\\ \textbf{Jesus:} Redesign the whole thing to work on small screen devices.
\\If time for it, Javascript: 
\begin{itemize}
	\item Add script to make transparent png pictures work in IE (older than vers. 9)
	\item Login
	\item Energy bars
	\item Indication of number of connected modules
	\item On / Off buttons to modules
\end{itemize}
\textbf{Theis:}
Design the page of the hub module (see the suggestion on dropbox). Add graph, text, on/off buttons etc.
\\Describe the reset.css file taken from blueprint.
\\\textbf{Dennis:}
Add bars and numbering to the modules on the index page.
\subsection{PRO3}
We have to make a rough plan of the future timeboxes.\\
\begin{tabular}{ | l | c | c | c |}
\hline
Description					& Type		& Time		& Depends\\\hline
Power line module			& Hardware	& xx:xx		& xx\\\hline
Power switch				& Hardware	& xx:xx		& xx\\\hline
Interface					& Hardware	& xx:xx		& xx\\\hline
ADC							& Hardware	& xx:xx		& xx\\\hline
Current sensor				& Hardware	& xx:xx		& xx\\\hline
Temperature sensor			& Hardware	& xx:xx		& xx\\\hline
Humidity sensor				& Hardware	& xx:xx		& xx\\\hline
Module connection			& Hardware	& xx:xx		& xx\\\hline
Grid module					& Hardware	& xx:xx		& xx\\\hline
Power line module			& Software	& xx:xx		& xx\\\hline
Power switch				& Software	& xx:xx		& xx\\\hline
Interface					& Software	& xx:xx		& xx\\\hline
ADC							& Software	& xx:xx		& xx\\\hline
Ethernet					& Software	& xx:xx		& xx\\\hline
Web server					& Software	& xx:xx		& xx\\\hline
Storage						& Software	& xx:xx		& xx\\\hline
Producer					& Software	& xx:xx		& xx\\\hline
Consumer					& Software	& xx:xx		& xx\\\hline
Main						& Software	& xx:xx		& xx\\\hline
\end{tabular}
\subsubsection{Timebox 1}
\begin{itemize}
\item Time: From week 48 to week 50.
\item Hand ins: Monday week 49 and Friday week 50.
\item Description: Estimate the total number of timeboxes. Make a rough selection of which parts will be developed in which timeboxes. From the rough selection, plan the manning of each timebox.
\item Note: Project week in week 48.
\end{itemize}

\subsubsection{Timebox 2}
\begin{itemize}
\item Time: From week 5 to week 6.
\item Hand ins: Friday week 6.
\item Description:
\item Note: EMC course in week 5.
\end{itemize}

\subsubsection{Timebox 3}
\begin{itemize}
\item Time: From week 7 to week 8.
\item Hand ins: Friday week 8.
\item Description:
\item Note:
\end{itemize}

\subsubsection{Timebox 4}
\begin{itemize}
\item Time: From week 9 to week 10.
\item Hand ins: Friday week 10.
\item Description:
\item Note: Climate date in week 10.
\end{itemize}

\subsubsection{Timebox 5}
\begin{itemize}
\item Time: From week 11 to week 12.
\item Hand ins: Friday week 12.
\item Description:
\item Note:
\end{itemize}

\subsubsection{Timebox 6}
\begin{itemize}
\item Time: From week 13 to week 14.
\item Hand ins: Friday week 14.
\item Description:
\item Note: Project week in week 13 and ester holiday at week 14.
\end{itemize}

\subsubsection{Timebox 7}
\begin{itemize}
\item Time: From week 15 to week 16.
\item Hand ins: Friday week 16.
\item Description:
\item Note:
\end{itemize}

\subsubsection{Timebox 8}
\begin{itemize}
\item Time: From week 17 to week 18.
\item Hand ins: Friday week 18.
\item Description:
\item Note:
\end{itemize}

\subsubsection{Timebox 9}
\begin{itemize}
\item Time: From week 19 to week 20.
\item Hand ins: Friday week 20.
\item Description:
\item Note: Project week in week 20.
\end{itemize}

\subsubsection{Timebox 10}
\begin{itemize}
\item Time: From week 21.
\item Hand ins: Friday week 21.
\item Description: Debug
\item Note: Project week in week 21.
\end{itemize}

\end{document}

