\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-1.5in}
\addtolength{\textheight}{1.75in}

\title{TeamUnix team rules}

\begin{document}
\maketitle

\section{Absence/Illness}
It is expected by every team member to meet to the first class every day (normally 8.20), 
if it is experienced that a member does not follow he will have to buy the other team-members beer (in the friday bar). 
\\If a member is sick or he by other reason can't be at school a day the notice should be done before the first class starts (normally 8:20), 
otherwise it counts just like if you are to late and you will have to buy the others beer.
\section{Meetings}
A 15 minutes meeting will occurs at least once a week, in a predefined time. The agenda of the team meeting is as follow: 
\begin{itemize}
	\item	 Delete Git files.
	\item  Project evolution
	\item Team matter stuffs
	\item Updates about when whom works and have other stuffs to do
\end{itemize}
The meetings on 3. semester is set to occur every wednesday from 11.02 to 11.33. Mainly the meetings will find place in Fablab (if it is not occurred). 
\section{Deadlines}
Each team member have to deliver his part at least 3 days before the deadline so it can be seen by all team members and corrections can be made if needed.
\section{Motivation}
The team will have gigantic burgers and a lot of beer to keep the motivation. Shu will be a plus and Underberg. 
\section{Exclusion of the team}
If you do not attempt the team meetings or if you become a big annoying Fred.
\section{Changes of the Team-rules}
If some changes in the team-rules should be done, it is done on the weekly meeting.
\end{document}
